Verb Meanings found in the ICB Corpus (top 200)

### 2022-01-26 prune/ICBEdataset_paper_InterCoderByLevels.Rmd
fixes

target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")

>>>>

target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")

### 2022-01-26 prune/ICBEdataset_paper_TableExampleSentenceCoding.Rmd
fixes

target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
sentence_example_sheet    <- readxl::read_excel(target_file, sheet="Sentence Tree Example Table")

>>>>

target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
sentence_example_sheet    <- readxl::read_excel(target_file, sheet="Sentence Tree Example Table")

### 2022-01-26 prune/ICBEdataset_paper_uncertainty.Rmd
fixes

```{r}
target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview,_trees_sentences.xlsx")
full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")

>>>>

```{r}
target_file <- paste0(here::here(),"/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx")
full_tree    <- readxl::read_excel(target_file, sheet="Codebook in Tree Form")

### 2022-01-26 replication_data/rmd/02_format_and_clean.rmd
fixes

temp_wide <- icb_long_clean2 %>%
             dplyr::select(icb_survey_version, email_id,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
             dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
             dplyr::mutate(variable_normalized= variable_normalized %>% trimws() %>% tolower()) %>%
             dplyr::filter(variable_normalized %in% (c( 'sentence_events', drops ) %>% trimws() %>% tolower()) ) %>%
             dplyr::distinct() %>% 
             dplyr::left_join(full_tree %>% 
                       dplyr::rename(value_normalized=leaf)  %>% 
                       dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) 
                       )

temp_long <- temp_wide %>% 
         dplyr::select(-variable_normalized,-value_normalized) %>%
         tidyr::pivot_longer(-c(icb_survey_version, email_id, crisno, sentence_number_int_aligned, section, sentence,   event_number_int,event_number_int_condition),
                      names_to='variable_normalized' , values_to= 'value_normalized')  %>%
         dplyr::filter(!is.na(value_normalized))

icb_long_clean_final <- icb_long_clean2 %>%
                   dplyr::select(icb_survey_version, email_id, crisno, sentence_number_int_aligned, section,  sentence,  event_number_int, event_number_int_condition, variable_normalized, value_normalized) %>%
                  rbind(temp_long) %>% dplyr::distinct() %>% 
                  dplyr::filter(!variable_normalized %in% drops)

>>>>

temp_wide <- icb_long_clean2 %>%
             dplyr::select(icb_survey_version, email_id, input_crisis,  crisno, sentence_number_int_aligned, section, sentence,event_number_int,  event_number_int_condition, variable_normalized, value_normalized) %>%
             dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) %>%
             dplyr::mutate(variable_normalized= variable_normalized %>% trimws() %>% tolower()) %>%
             dplyr::filter(variable_normalized %in% (c( 'sentence_events', drops ) %>% trimws() %>% tolower()) ) %>%
             dplyr::distinct() %>% 
             dplyr::left_join(full_tree %>% 
                       dplyr::rename(value_normalized=leaf)  %>% 
                       dplyr::mutate(value_normalized= value_normalized %>% trimws() %>% tolower()) 
                       )

temp_long <- temp_wide %>% 
         dplyr::select(-variable_normalized,-value_normalized) %>%
         tidyr::pivot_longer(-c(icb_survey_version, email_id,  input_crisis, crisno, sentence_number_int_aligned, section, sentence,   event_number_int,event_number_int_condition),
                      names_to='variable_normalized' , values_to= 'value_normalized')  %>%
         dplyr::filter(!is.na(value_normalized))

icb_long_clean_final <- icb_long_clean2 %>%
                   dplyr::select(icb_survey_version, email_id, input_crisis, crisno, sentence_number_int_aligned, section,  sentence,  event_number_int, event_number_int_condition, variable_normalized, value_normalized) %>%
                  rbind(temp_long) %>% dplyr::distinct() %>% 
                  dplyr::filter(!variable_normalized %in% drops)

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_appendixICBCrises.Rmd
fixes

```{r include=F}
#Load the ICB wide codings
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_crc32)) %>% dplyr::select(crisno, email_crc32) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)

@@

avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_crc32)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)

>>>>

```{r include=F}
# #Load the ICB wide codings
icb_wide_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_wide_clean.Rds"))
n_crisis <- icb_wide_clean %>% dplyr::select(crisno) %>% unique() %>% nrow()
n_sentences <- icb_wide_clean %>% dplyr::select(crisno, sentence_number_int_aligned) %>% unique() %>% nrow()
n_events <- icb_wide_clean %>% dplyr::filter(event_number_int %in% c(1,2,3)) %>% nrow()
n_events_cuba <- icb_wide_clean %>% dplyr::filter(crisno == 196 & event_number_int %in% c(1,2,3)) %>% nrow()
n_coders <- icb_wide_clean %>% dplyr::select(email_id) %>% unique() %>% nrow()

avg_coders_per_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::select(crisno, email_id) %>% unique() %>% dplyr::count(crisno) %>% dplyr::select(n) %>% lapply(mean)

@@

avg_events_per_coder_crisis <- icb_wide_clean %>% dplyr::filter(crisno != 196) %>% dplyr::mutate(cris_coder = paste(crisno, email_id)) %>% dplyr::count(cris_coder) %>% dplyr::select(n) %>% lapply(mean)

### 2022-01-26 replication_paper/rmd/ICBEdataset_paper_appendixVerbMeanings.Rmd
fixes

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")

>>>>

target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors    <- readxl::read_excel(target_file, sheet="actors")
